Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip

### 2014-02-18 PAPER/introduction.tex
general fixing

The \disr{} approach presented in this work is a first attempt to
achieve the same goals of a segment based turn prohibition without
requiring neither the knowledge of a topology graph nor centralized execution. In particular
\disr{} implements segment discovery and turn prohibition using a
completely different mechanism, based on a distributed exchange of
small setup packets requiring on average $15\%$ of the available
resource budget. The following main features distinguish \disr{}
from classic approaches to segment partitioning: 
\begin{itemize}
\item No centralized entity is globally responsible and/or aware of
what is going on, i.e. the status of the \disr{} execution is
collectively distributed among the nodes
\item  No defect map and/or topology graph is used as input,
thus, the topology has to be discovered \emph{while} segments are
created
\item At the end of the execution, no segment list is created or
stored anywhere: each node is only aware of belonging to \hl{a segment | some segments},
ignoring the presence of other nodes in the same segment and also the
presence of other segments in the network
\end{itemize}

>>>>

The \disr{} approach presented in this work is a first attempt to
achieve the same goals of a segment based turn prohibition without
requiring neither the knowledge of a topology graph nor centralized execution. In particular
\disr{} implements segment discovery and turn prohibition using a
completely different mechanism, based on a distributed exchange of
small setup packets requiring on average $15\%$ of the available
resource budget. The following main features distinguish \disr{}
from classic approaches to segment partitioning: 
\begin{itemize}
\item No centralized entity is globally responsible and/or aware of
what is going on, i.e. the status of the \disr{} execution is
collectively distributed among the nodes.
\item  No defect map and/or topology graph is used as input,
thus, the topology has to be discovered \emph{while} segments are
created.
\item At the end of the execution, no segment list is created or
stored anywhere: each node is only aware of belonging to \hl{a segment | some segments},
ignoring the presence of other nodes in the same segment and also the
presence of other segments in the network.
\end{itemize}
